paper3

### 2022-07-25 paper3.Rmd
Bayesian Ranking

rm(list = c("installed_packages", "packages"))
```

@@

## Download Scenic-Or-Not data
sc1 <- read_tsv("http://scenicornot.datasciencelab.co.uk/votes.tsv",
               col_types = cols("ID" = col_number(),
                                "Lat" = col_double(),
                                "Lon" = col_double(),
                                "Average" = col_double(),
                                "Variance" = col_double(),
                                "Votes" = col_character(),
                                "Geograph URI" = col_character())) %>%
  rowwise() %>%
  mutate(Mean = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% mean(),
         Median = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% median(),
         Variance = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% var(),
         Entropy = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% entropy(),
         Number = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% length(),
           `10` = Votes %>% strsplit(",") %>% unlist() %>% str_count("10") %>% sum(),
            `9` = Votes %>% strsplit(",") %>% unlist() %>% str_count("9") %>% sum(),
            `8` = Votes %>% strsplit(",") %>% unlist() %>% str_count("8") %>% sum(),
            `7` = Votes %>% strsplit(",") %>% unlist() %>% str_count("7") %>% sum(),
            `6` = Votes %>% strsplit(",") %>% unlist() %>% str_count("6") %>% sum(),
            `5` = Votes %>% strsplit(",") %>% unlist() %>% str_count("5") %>% sum(),
            `4` = Votes %>% strsplit(",") %>% unlist() %>% str_count("4") %>% sum(),
            `3` = Votes %>% strsplit(",") %>% unlist() %>% str_count("3") %>% sum(),
            `2` = Votes %>% strsplit(",") %>% unlist() %>% str_count("2") %>% sum(),
            `1` = Votes %>% strsplit(",") %>% unlist() %>% str_count("1") %>% sum())%>%
  mutate(`1` = `1`-`10`) %>%
  st_as_sf(coords = c("Lon","Lat"), crs = 4326) %>%
  st_transform(crs = 27700)
```

```{python}
import math
from scipy import stats

def ci_lower_bound(positive_ratings, total_ratings, confidence):
    """
    Following http://www.evanmiller.org/how-not-to-sort-by-average-rating.html#changes
    :return: the lower bound of the confidence interval
    """
    n =  total_ratings
    z = stats.norm.ppf(1 - (1 - confidence) / 2)
    p_hat = 1.0 * positive_ratings / n
    result = (
        (
             p_hat + z * z / (2 * n)
             - z * math.sqrt(
                 (p_hat * (1 - p_hat) + z * z / (4 * n)) / n
             )
        ) / (1 + z * z / n)
    )
    return result

```

```{r}
LANDMAP <- sc %>% 
  st_join(VS, .) %>% 
  aggregate(Votes~UID, data = ., paste0, collapse = ",") %>%
  merge(VS, ., by = "UID", all = T) %>%
  as_tibble() %>% 
  st_as_sf() %>%
  rowwise() %>%
  mutate(Scenicness.mean_all = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% mean(),
         Scenicness.median_all = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% median(),
         Scenicness.entropy_all = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% entropy(),
         Scenicness.number_all = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% na.omit() %>% length()) %>%
  ungroup()

@@

LANDMAP <- sc %>%
  st_join(LANDMAP, .) %>%
  aggregate(Mean~UID, data = ., paste0, collapse = ",") %>%
  merge(LANDMAP, ., by = "UID", all = T) %>%
  as_tibble() %>%
  st_as_sf() %>%
  rowwise() %>%
  mutate(Scenicness.mean_of_mean = Mean %>% strsplit(",") %>% unlist() %>% as.numeric() %>% mean(),
         Scenicness.median_of_mean = Mean %>% strsplit(",") %>% unlist() %>% as.numeric() %>% median(),
         Consultant = ifelse(str_detect(VS_1a, "Bronwen Thomas"), "B", "A")) %>%
  dplyr::select(UID, CLS_1, CLS_2, CLS_3, CLS_4, ScenicQuality, Consultant, 
                Votes, Scenicness.mean_all, Scenicness.median_all, Scenicness.entropy_all, Scenicness.number_all,
                Scenicness.mean_of_median, Scenicness.median_of_median,
                Scenicness.mean_of_mean, Scenicness.median_of_mean) %>%
  ungroup()

plot(LANDMAP["ScenicQuality"], border = 'NA', key.pos = 1)  
```

@@

LANDMAP <- st_transform(LANDMAP, crs = st_crs(Wildness)) %>%
  exact_extract(Wildness, ., fun = c('mean', 'median', 'coefficient_of_variation', 'variance', 'quantile'), quantiles = c(0.25, 0.75)) %>%
  mutate(Wildness.iqr = q75 - q25) %>%
  dplyr::select(Wildness.mean = mean, Wildness.median = median, Wildness.iqr, Wildness.cv = coefficient_of_variation, Wildness.variance = variance) %>%
  bind_cols(LANDMAP[, 1:13], .) %>%
  st_transform(crs = 27700)

@@

# split train/test set
# X = landmap_B.loc[:, ['Scenicness.median', 'Scenicness.entropy', 
#                       'Wildness.median', 'Wildness.variance',
#                       'x', 'y']]

X = landmap_B.loc[:, ['Scenicness.mean', 'Wildness.mean']]
y = landmap_B.loc[:, ['ScenicQuality']]

>>>>

rm(list = c("installed_packages", "packages"))
```
## Bayesian XXX by Evan Miller
Where zα/2 is the 1−α/2 quantile of a normal distribution.

```{r Bayesian Ranking}
"
Following https://www.evanmiller.org/ranking-items-with-star-ratings.html
return: the lower bound of the confidence interval
"
BayesRank <- function(votes, K, α = .05){
  N = votes %>% strsplit(",") %>% unlist() %>% length() # total_ratings
  s_k = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10) %>% array(dim = c(1, 10))
  n_k = votes %>%
    strsplit(",") %>% 
    unlist() %>%
    as.numeric() %>%
    tabulate(nbins = 10) %>%
    array(dim = c(10, 1))
  # 1-α: confidence level (commonly 90%, 95% or 99%)
  # confidence level 90%: α = 0.1  -> z_α/2 = z_0.05 = 1.645
  # confidence level 95%: α = 0.05 -> z_α/2 = z_0.025= 1.96
  # confidence level 99%: α = 0.01 -> z_α/2 = z_0.005= 2.576
  # z is the standard normal random variable. z_α/2 is the α/2 quantile of its distribution which means     critical value.
  z = qnorm(1-α/2)
  S = s_k %*% (n_k + 1)/(N + K) - 
  z*sqrt((s_k^2 %*% (n_k + 1)/(N + K) - (s_k %*% (n_k + 1)/(N + K))^2)/(N + K + 1))
  S = as.numeric(S)
  return(S)
}
```

@@

## Download Scenic-Or-Not data
sc <- read_tsv("http://scenicornot.datasciencelab.co.uk/votes.tsv",
               col_types = cols("ID" = col_number(),
                                "Lat" = col_double(),
                                "Lon" = col_double(),
                                "Average" = col_double(),
                                "Variance" = col_double(),
                                "Votes" = col_character(),
                                "Geograph URI" = col_character())) %>%
  rowwise() %>%
  mutate(Mean = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% mean(),
         Median = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% median(),
         Variance = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% var(),
         Entropy = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% entropy(),
         BayeScore = Votes %>% BayesRank(K = 10, α = .05))%>%
  st_as_sf(coords = c("Lon","Lat"), crs = 4326) %>%
  st_transform(crs = 27700)
```

```{r}
LANDMAP <- sc %>% 
  st_join(VS, .) %>% 
  aggregate(Votes~UID, data = ., paste0, collapse = ",") %>%
  merge(VS, ., by = "UID", all = T) %>%
  as_tibble() %>% 
  st_as_sf() %>%
  rowwise() %>%
  mutate(Scenicness.mean_of_all = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% mean(),
         Scenicness.median_of_all = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% median(),
         Scenicness.entropy_of_all = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% entropy(),
         Scenicness.number_of_all = Votes %>% strsplit(",") %>% unlist() %>% as.numeric() %>% na.omit() %>% length()) %>%
  ungroup()

@@

LANDMAP <- sc %>%
  st_join(LANDMAP, .) %>%
  aggregate(Mean~UID, data = ., paste0, collapse = ",") %>%
  merge(LANDMAP, ., by = "UID", all = T) %>%
  as_tibble() %>%
  st_as_sf() %>%
  rowwise() %>%
  mutate(Scenicness.mean_of_mean = Mean %>% strsplit(",") %>% unlist() %>% as.numeric() %>% mean(),
         Scenicness.median_of_mean = Mean %>% strsplit(",") %>% unlist() %>% as.numeric() %>% median()) %>%
  ungroup()

LANDMAP <- sc %>%
  st_join(LANDMAP, .) %>%
  aggregate(BayeScore~UID, data = ., paste0, collapse = ",") %>%
  merge(LANDMAP, ., by = "UID", all = T) %>%
  as_tibble() %>%
  st_as_sf() %>%
  rowwise() %>%
  mutate(Scenicness.mean_of_bayescore = BayeScore %>% strsplit(",") %>% unlist() %>% as.numeric() %>% mean(),
         Scenicness.median_of_bayescore = BayeScore %>% strsplit(",") %>% unlist() %>% as.numeric() %>% median(),
         Consultant = ifelse(str_detect(VS_1a, "Bronwen Thomas"), "B", "A")) %>%
  ungroup()

plot(LANDMAP["ScenicQuality"], border = 'NA', col = RColorBrewer::brewer.pal(4, "YlOrBr"), key.pos = 1)  
```

@@

LANDMAP <- st_transform(LANDMAP, crs = st_crs(Wildness)) %>%
  exact_extract(Wildness, ., 
                fun = c('mean', 'median', 'coefficient_of_variation', 'variance', 'quantile'), 
                quantiles = c(0.25, 0.75)) %>%
  mutate(Wildness.iqr = q75 - q25) %>%
  bind_cols(LANDMAP, .) %>%
  dplyr::select(UID, CLS_1, CLS_2, CLS_3, CLS_4, ScenicQuality, Consultant,
                Votes, Scenicness.mean_of_all, Scenicness.median_of_all,
                Scenicness.entropy_of_all, Scenicness.number_of_all,
                Scenicness.mean_of_median, Scenicness.median_of_median,
                Scenicness.mean_of_mean, Scenicness.median_of_mean,
                Scenicness.mean_of_bayescore, Scenicness.median_of_bayescore,
                Wildness.mean = mean, Wildness.median = median, Wildness.iqr, 
                Wildness.cv = coefficient_of_variation, Wildness.variance = variance) %>%
  st_transform(crs = 27700)

@@

# split train/test set
# X = landmap_B.loc[:, ['Scenicness.mean', 'Wildness.mean']]
X = landmap_B.loc[:, ['Scenicness.median', 'x', 'y']]
y = landmap_B.loc[:, ['ScenicQuality']]
